### 2015-07-07 Irregular-occ/Irregular-occ.tex
.

\author{ A. R. Gomes-Júnior
          \inst{1},
          M. Assafin 
          \inst{1} \fnmsep\thanks{Affiliated researcher at Observatoire de Paris/IMCCE, 77 Avenue Denfert Rochereau 75014 Paris, France},
          R. Vieira-Martins
          \inst{1,2,3} \fnmsep\thanks{Affiliated researcher at Observatoire de Paris/IMCCE, 77 Avenue Denfert Rochereau 75014 Paris, France},
%          J.-E. Arlot
%          \inst{4},      
          J. I. B. Camargo
          \inst{2,3},     
          F. Braga-Ribas
          \inst{2,4}, 
%          D. N. da Silva Neto
%          \inst{6},
%          A. H. Andrei
%          \inst{1,2} \fnmsep\thanks{Affiliated researcher at Observatoire de Paris/SYRTE, 77 Avenue Denfert Rochereau, 75014 Paris, France},
          A. Dias-Oliveira
          \inst{2},
          B. E. Morgado
          \inst{1},
          G. Benedetti-Rossi
          \inst{2},
%          Y. Duchemin
%          \inst{4,7},
%          J. Desmars
%          \inst{4},
%          V. Lainey
%          \inst{4},
%          W. Thuillot
%          \inst{4}
          }

@@

In the intent to obtain their physical parameters (size, shape, albedo, density, etc) and help identify their origin locations, we will make use of the stellar occultation technique. This technique is the best one to obtain the physical parameters of the solar system objects from ground-based observations providing more accurate results than other techniques \citep{Sicardy2011, Ortiz2012, Braga-Ribas2014}.

>>>>

\author{ A. R. Gomes-Júnior
          \inst{1},
          M. Assafin 
          \inst{1} \fnmsep\thanks{Affiliated researcher at Observatoire de Paris/IMCCE, 77 Avenue Denfert Rochereau 75014 Paris, France},
          R. Vieira-Martins
          \inst{1,2,3} \fnmsep\thanks{Affiliated researcher at Observatoire de Paris/IMCCE, 77 Avenue Denfert Rochereau 75014 Paris, France},
%          J.-E. Arlot
%          \inst{4},      
          J. I. B. Camargo
          \inst{2,3},     
          F. Braga-Ribas
          \inst{2,4}, 
%          D. N. da Silva Neto
%          \inst{6},
%          A. H. Andrei
%          \inst{1,2} \fnmsep\thanks{Affiliated researcher at Observatoire de Paris/SYRTE, 77 Avenue Denfert Rochereau, 75014 Paris, France},
          B. E. Morgado
          \inst{1},
          A. Dias-Oliveira
          \inst{2},
          G. Benedetti-Rossi
          \inst{2},
%          Y. Duchemin
%          \inst{4,7},
%          J. Desmars
%          \inst{4},
%          V. Lainey
%          \inst{4},
%          W. Thuillot
%          \inst{4}
          }

@@

In the intent to obtain their physical parameters (size, shape, albedo, density, etc) and help identify their origin locations, we will make use of the stellar occultation technique. This technique is the best one to obtain the physical parameters of the solar system objects from ground-based observations providing more accurate results than other groud-based techniques \citep{Sicardy2011, Ortiz2012, Braga-Ribas2014}.
